A Spatial AR System for Axis-aligned Augmentation of Planar Scenes in Industrial Settings

### 2021-07-14 paper/elsarticle/elsarticle-template.tex
paper

Keystone correction for planar scenes can be carried out using a 2D homography \cite{Hartley2004}---an invertible transformation that preserves colinearity, hence alternatively termed a `colineation'---and is ultimately the approach we take as well. One approach to calibrating a projector-camera system in a fully automatic fashion using a homography reduces to automatically establishing keypoint matches between the image to be projected in the projector's image plane and the projected image in the camera's image plane, and then to use those matches to automatically compute the homography that warps the one image to the other \cite{sukthankar2001smarter}. While such an approach could be extended to enable placement to multiple locations in accordance with a steerable mirror \cite{okatani2005autocalibration}, relying on keypoint matches alone does not enable reasoning about the target dimensions of augmentations in metric terms, or offer the convenience of placing annotations in terms of the principal axes of camera facing the scene plane.

@@

>>>>

Keystone correction for planar scenes can be carried out using a 2D homography \cite{Hartley2004}---an invertible transformation that preserves colinearity, hence alternatively termed a `colineation'---and is ultimately the approach we take as well. The intuition for why a transformation that maps lines to lines can serve to model the necessary image warp can be drawn from considering a planar chessboard pattern: looking at an image of a chessboard acquired from an oblique angle, one observes that parallel lines appear to meet in respective vanishing points; looking at an image of the same chessboard acquired frontally with respect to the plane of the chessboard, lines parallel in the chessboard appear parallel in the image (i.e., they are said to meet `at infinity'). To warp the former image (where lines parallel in the scene meet in respective vanishing points) such that the lines of the chessboard appear as in the latter image (where lines parallel in the scene meet at infinity), a transformation that maps lines to lines that would give the desired effect.

One approach to calibrating a projector-camera system in a fully automatic fashion using a homography reduces to (i) automatically establishing keypoint matches between the image to be projected in the projector's image plane and the projected image in the camera's image plane, and then to (ii) using those matches to automatically compute the homography that warps the one image to the other \cite{sukthankar2001smarter}. Relying on keypoint matches alone, however, does not enable reasoning about the target dimensions of augmentations in metric terms, or offer the convenience of placing annotations in terms of the principal axes of camera facing the scene plane. For this, calibration of the camera and of the projector is necessary: \cite{raskar2001self}...

@@

Mention circles pattern: \cite{chiu2011novel}

...
